Contribution Title\thanks{Supported by organization x.}

### 2019-12-16 sections/evaluation.tex
fix typo, add a follow up question

$\IUIP$ learning schemes show marginal improvement on $\MapleNineShort$. Despite significantly reducing clause size,  only two out of four configurations improved solved instances by 1 and 2 instances, respectively. $\MapleNineShort$ remembers previously learned clauses, and prioritize the clause if the same clause (denote as duplicate clause) is learned again later. $\IUIP$ and duplicate learning (DL) didn't synergies well possibly because multiple 1-UIP clause can be derived to the same i-UIP clause through the $\IUIP$; therefore, duplicate clauses could appear too frequently for duplicate learning to prioritize the right clauses.

>>>>

$\IUIP$ learning schemes show marginal improvement for $\MapleNineShort$. Despite significantly reducing clause size,  only two out of four configurations improved solved instances by 1 and 2 instances, respectively. $\MapleNineShort$ uses duplicate learning (DL) to prioritize clauses that are learned multiple times. $\IUIP$ and DL didn't synergies well possibly because different 1-UIP clause can be reduced to the same i-UIP clause through the $\IUIP$ learning; therefore, DL could encounter too many duplicate i-uip clauses to correctly prioritize the important clauses. \nf{should I run some experiment to validate my guess?, if the guess is valid, should I adjust DL settings to make it compatible with $\IUIP$}
